Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-16 manuscript/climate_sensitivity_draft.Rmd
Added small updates to text and table

Debates have also arisen regarding the traits influencing tree growth responses to drought. Studies within temperate broadleaf forests have observed ring-porous species showing higher drought tolerance than diffuse-porous species [@friedrichs_species-specific_2009; @elliott_forest_2015; @kannenberg_linking_2019], but this distinction does not always hold [@martin-benito_convergence_2015], would not hold in the global context [@wheeler_variations_2007; @olson_xylem_2020] and does not resolve differences among the many species within each category. Commonly-measured traits including wood density and leaf mass per area ($LMA$) have been linked to drought responses within some temperate deciduous forests [@abrams_adaptations_1990; @guerfel_impacts_2009; @hoffmann_hydraulic_2011; @martinbenito_convergence_2015] and across forests worldwide [@greenwood_tree_2017]. However, in other cases these traits could not explain drought tolerance [e.g., in a tropical rainforest; @marechaux_leaf_2019], or the direction of response was not always consistent. For instance, higher wood density has been associated with greater drought resistance at a global scale [@greenwood_tree_2017], but correlated negatively with tree performance during drought in a broadleaf deciduous forest in the southeastern United States [@hoffmann_hydraulic_2011]. Thus, the perceived influence of these traits on drought resistance may actually reflect indirect correlations with other traits that more directly drive drought responses [@hoffmann_hydraulic_2011].

@@

Analyses focused on testing the predictions presented in Table 1 with $Rt$ (or $Rt_{ARIMA}$), $Rc$, or $Rs$ as the response variable. 
Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a mixed effects model, implemented in the lme4 package in R [@R-lme4].
In the multi-year model, we included a random effect of tree nested within species and a fixed effect of drought year to represent the combined effects of differences in drought characteristics.
Individual year models included a random effect of species. 
All models included fixed effects of independent variables of interest (Tables 1,3) as specified below.
All variables across all best models had variance inflation factors <1.2 (1 +/- 0.019). 
We used Akaike information criterion with correction for small sample sizes [AICc; see @brewer_relative_2016] to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
Individual model terms were considered significant when their addition to a model improved fit at $\Delta$AICc $\ge$ 2.0, where $\Delta$AICc is the difference in AICc between models with and without the trait.

>>>>

Debates have also arisen regarding the traits influencing tree growth responses to drought. Studies within temperate broadleaf forests have observed ring-porous species showing higher drought tolerance than diffuse-porous species [@friedrichs_species-specific_2009; @elliott_forest_2015; @kannenberg_linking_2019], but this distinction does not always hold [@martin-benito_convergence_2015], nor does it hold in the global context [@wheeler_variations_2007; @olson_xylem_2020], and it does not resolve differences among the many species within each category. Commonly-measured traits including wood density and leaf mass per area ($LMA$) have been linked to drought responses within some temperate deciduous forests [@abrams_adaptations_1990; @guerfel_impacts_2009; @hoffmann_hydraulic_2011; @martinbenito_convergence_2015] and across forests worldwide [@greenwood_tree_2017]. However, in other cases these traits could not explain drought tolerance [e.g., in a tropical rainforest; @marechaux_leaf_2019], or the direction of response was not always consistent. For instance, higher wood density has been associated with greater drought resistance at a global scale [@greenwood_tree_2017], but correlated negatively with tree performance during drought in a broadleaf deciduous forest in the southeastern United States [@hoffmann_hydraulic_2011]. Thus, the perceived influence of these traits on drought resistance may actually reflect indirect correlations with other traits that more directly drive drought responses [@hoffmann_hydraulic_2011].

@@

Analyses focused on testing the predictions presented in Table 1 with $Rt$ (or $Rt_{ARIMA}$), $Rc$, or $Rs$ as the response variable. 
Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a mixed effects model, implemented in the lme4 package in R [@R-lme4].
In the multi-year model, we included a random effect of tree nested within species and a fixed effect of drought year to represent the combined effects of differences in drought characteristics.
Individual year models included a random effect of species. 
All models included fixed effects of independent variables of interest (Tables 1,3) as specified below.
All variables across all best models had variance inflation factors between 1 and 1.045.
We used Akaike information criterion with correction for small sample sizes [AICc; see @brewer_relative_2016] to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
Individual model terms were considered significant when their addition to a model improved fit at $\Delta$AICc $\ge$ 2.0, where $\Delta$AICc is the difference in AICc between models with and without the trait.
